Concretizing the Process Hitting into Biological Regulatory Networks

### 2013-04-17 parts/infer-param.tex
finish updating notations in parameters inference

This subsection presents some results related to the inference of independent discrete parameters from a given PH. These results are equivalent to those presented in \cite{PMR10-TCSB}, with notation adapted to be shared with the previous section.
In addition, we introduce the well-formed PH for parameter inference property (\pref{pro:wf-ph-K}),
which implies that the inferred IG does not contain any unsigned interactions, and thus can be seen as the
regular IG $(\Gamma, E_+, E_-)$,
and that any processes in $\levelsA{b}{a}$ (resp. $\levelsI{b}{a}$) share the same behavior
regarding $a$.

@@

\begin{example*}
Applied to the PH in \pref{fig:runningPH-1}, we obtain, for instance, 
$K_{b,\{a\},\emptyset} = [0 ; 1]$ and
$K_{a,\{b,c\},\emptyset} = [2 ; 2]$,
while $K_{a,\{b\},\{c\}}$ can not be inferred.
For the PH in \pref{fig:runningPH-2}, this latter is evaluated to $[1;1]$.
\end{example*}

>>>>

This subsection presents some results related to the inference of independent discrete parameters from a given PH.
These results are equivalent to those presented in \cite{PMR10-TCSB}, with notation adapted to be shared with the previous section.
In addition, we introduce the well-formed PH for parameter inference property (\pref{pro:wf-ph-K}),
which implies that the inferred IG does not contain any unsigned interactions, and thus can be seen as the
regular IG $(\Gamma, E)$,
and that any processes in $\levels{b}{a}$ (resp. $\ulevels{b}{a}$) share the same behavior
regarding $a$.

@@

\begin{example*}
Applied to the PH in \pref{fig:runningPH-1}, we obtain, for instance, 
$K_{b,\emptyset} = [0 ; 1]$ and
$K_{a,\{b,c\}} = [2 ; 2]$,
while $K_{a,\{b\}}$ can not be inferred.
For the PH in \pref{fig:runningPH-2}, this latter is evaluated to $[1;1]$.
\end{example*}
